---
title: "Using the Grammar of Hypothesis"
author: "Using the Grammar of Hypothesis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(hypegrammaR)
mydata<-read.csv("../tests/testthat/data.csv")

```
##
define your survey design. Since it's a simple random design, we just pass the data and that's all. Now R knows that we're doing simple random sampling, so no need to bother with cluster/stratification stuff.

```{r}
mydesign<-map_to_design(mydata)

# hypegrammaR:::barchart_with_error_bars(hypothesis.test.results = result$hypothesis.test,
#                                        summary.statistics = result$summary.statistic)

```

Say my research question is whether there is a difference in nutrition need between different regions.
this means I want to get


The function `analyse_indicator` does the heavy lifting. It wants to know:
  - the general case of analysis that you want to do. Currently available are
      - `direct_reporting`: simply calculate the summary statistic (categorical or numerical)
      - `group_difference`: looking for differences between groups (categorical or numerical)
      
```{r}

case<-map_to_case(data,
                  dependent.var = "nutrition_need",
                  independent.var = "region",hypothesis.type = "group_difference")





```
### Analyse Indicator


