---
title: "Example MSNA"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example MSNA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```


## Main Steps

- once: setup github repository
- once: install packages
- load packages
- load inputs from csv files
- preprocess inputs
- make sure all inputs can be matched
- create analysisplan
- run analysisplan
- export results

## Details

### DEFINE YOUR ANALYSIS

- create analysisplan 
- create recoding plan
- add newly created variables to kobo tool - to pretend they had been collected

### LOAD PACKAGES


```{r}
library(koboquest)
library(hypegrammaR)
library(composr)
library(kobostandards)
library(dplyr)
library(xlsformfill)
```


### PREPARE INPUTS

- load inputs _as data.frames_ from csv
    - questionnaire questions sheet ("questions") (excel -> save active sheet as csv)
    - questionnaire choices sheet ("choices")
        - add external choices to the regular choices sheet
        - replace "select_one_external" and "select_multiple_external" by "select_one"
    - analysisplan
    - recoding plan
    - data
    - sampling frame
- (Generate data)
- create koboquest questionnaire object

```{r}
mydata <- read.csv("./input/data.csv", stringsAsFactors = F)
...

```

```{r}
mydata <- xlsform_fill(questions,choices,1000)

```

```{r}
load_questionnaire(mydata, questions, choices)
```
### RECODING

- batch recode from recodingplan



### SAMPLING STRATEGY PREPARATIONS
- stratification weighting:
    - create a data variable whos values match _exactly_ the strata names in the sampling frame
        - for _all_ stratification elements: districts & population groups!
- (cluster weighting: maybe.. depending on sampling strategy)
    - same as stratitifaction
    - use surveyweights::combine_weighting_functions() to combine weighting functions
- Create unique cluster id variable in the data
- create weighting function (map_to_weighting) -> weighting

```{r}

samplingframe_tidy<- samplingframe_tidy %>%
  mutate(stratum_id = paste0(district.pcode,"_",population_group))


data <- data %>%
  mutate(data_stratum_id = paste0("YE",
                                  a3_metadata,
                                  "_",
                                  data_stratum_id))  

```

### RAW RESULTS

- from analysisplan map to outputs ==> analysisplan_outputs
    - _Recoded_ data
    - analysisplan
    - weighting
    - cluster id variable name
    - questionnaire

```{r}


results <- from_analysisplan_map_to_output(response, analysisplan = analysisplan[1:20,],
                                           weighting = strata_weight_fun,
                                           cluster_variable_name = NULL,
                                           questionnaire)
```


### FINAL OUTPUTS
- individual results
    - map_to_visualisation
    - map_to_table
    - map_to_labeled
- list of results (analysisplan_outputs$results)
    - lapply(map_to_visualisation)
    - lapply(map_to_table)
    - lapply(map_to_labeled)
- **analysisplan_outputs**
    - hypegrammaR:::map_to_generic_hierarchical_html
        - FUNCTION TO TURN RESULT INTO MARKDOWN
            - hypegrammaR:::from_result_map_to_md_table
            - map_to_md_hypothesis_test(result)
        - analysisplan columns you want to use to structure output
        - prefixes for these when they become headlines
        - level = 2
        - questionnaire
        - output directory
        - output file

```{r}


map_to_hierarchical_template(results,
                             questionnaire = questionnaire,
                             by_analysisplan_columns =c("dependent.var"
                                                        # ,"repeat.var"
                                                        # ,"repeat.var.value"
                                                        # ,"independent.var",
                                                        # ,"independent.var.value"
                             ),
                             filename = "./output/test.html")


browseURL("./output/test.html")

map_to_master_table(results,"test.csv")
```







