---
title: "Quickstart"
author: "Martin Barner / Eliora Henzler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = F,
  comment = "#>"
)
```
## Pretext
The hypegrammaR package implements the [IMPACT quantitative data analysis guidelines](http://example.com). While this guide works on its own, all of this will make a lot more sense if you read those first.

## What you need:
get all your files in csv format first:

  - your data as a csv file
  - your sampling frame(s) as csv file(s) if the analysis needs to be weighted
  
  - your kobo questionnaire questions and choices sheets as two csv files; Necessary if you have select_multiple questions, skip logic or want to use the labels.



> _**IMPORTANT NOTE:**_ your data and questionnaire must adhere to the standard xml style output from kobo otherwise this will either not work or produce wrong results.
>
> - column headers unchanged
> - questionnaire names unchanged
> - xml values (NOT labeled)
> - select_multiple questions have one column with all responses concatenated (separated by blank space " "), and one column for each response named [question name].[choice name]
>
> Your sampling frame must be in the correct format:
>
> - must have one row per stratum; one column for population numbers; one column for strata names
> - The values in the column with the strata names must appear exactly identical in a column in the data

## Preparation
#### Install the hypegrammaR package
This line you only have to run _once_ when using hypegrammaR for the first time, or to update to a new version.
```{r,eval=F}
devtools::install_github("ellieallien/hypegrammaR",build_opts = c(), ref = "master")

```
(the `build_opts = c()` makes sure the package includes all extra help pages & documentation)
For this step only, you need a more or less stable internet connection.

#### Load the hypegrammaR package
```{r,warning=FALSE,message=FALSE, eval = F}
library(hypegrammaR)
library(koboquest)
```

#### Load your files


##### The data
`load_data` takes only one argument `file`, the path to the csv file. 
```{r}
assessment_data<-load_data(file = "../data/testdata.csv")
```
Conditions:

- it must adhere to standard kobo xml format
- it must _not_ contain labeled values
- it must have a _single_ row for column headers (unchanged as they come out of kobo)
- it may contain additional columns that were not in the original questionnaire. It is good practice to additional new variables as additional rows to the questionnaire, specifying variable type, choices etc.

##### Load the sampling frame

This is only necessary if the analysis needs to be weighted.

The sampling frame should be a csv file with one column with strata names, one column with population numbers.
`load_samplingframe` takes only one argument `file`, the path to the csv file. 

```{r}

sampling_frame<-load_samplingframe(file = "../data/test_samplingframe.csv")
```

Now turn your sampling frame into a weighting function with `map_to_weighting`. We see that the relevant columns in the sampling frame are called "strata names" and "population". The column in the data correspoinding to the strata names is called "stratification" in this data set. We need to supply these column names as arguments to `map_to_weighing`:

```{r}
myweighter<-map_to_weighting(sampling.frame = sampling_frame,
                             data.stratum.column = "stratification",
                             sampling.frame.population.column = "population",
                             sampling.frame.stratum.column = "strata.names", 
                             data = assessment_data)
```

##### The Questionnaire
Finally the questionnaire, which depends on the question and the choices sheet as a csv.
hypegrammaR can live without this, but a questionnaire is necessary for correct analysis of select_multiple questions.

The parameters are:

- `data`: the object that stores the data loaded above
- `questions.file`: the path to the questions sheet as a csv file
- `choices.file` the path to the choices sheet as a csv file
- `choices.label.column.to.use`: the exact name of the column containing the labels that should be used. You can add an extra column with custom labels to your choices sheet if you don't want to use the choice labels from the original questionnaire

```{r}
questionnaire<- koboquest::load_questionnaire(data = assessment_data,
                                  questions = "../data/test_questionnaire_questions.csv",
                                  choices = "../data/test_questionnaire_choices.csv",
                                  choices.label.column.to.use = "label::English"
                                             )

```
Conditions:

- Both the choices and questions csv files should be exact copies of the respective sheets in the kobo xml form (except for the additions mentioned above.)

### Analysis

#### Identify your analysis parameters

- what are the column headers of your dependent and independent variables, and what are their data types?
    - this Example: *"sourceexpenses" (categorical)* and *"informalsettlement" (categorical)*
- what type of hypothesis do you have?
    - this Example: the *difference between groups*

#### map to the analysis case
For this example, our hypothesis is that idp or refugee households received different assistance compared host community hh.


```{r}
my_case<-map_to_case(hypothesis.type = "group_difference",
                  dependent.var.type = "numerical",
                  independent.var.type =  "categorical")


```


You can find out what exactly you can/should enter for these parameters by running `?map_to_case`, which will open the help page for the function (this works for any function)

#### Run the analysis

Now you use the inputs loaded above to an analysis result:
```{r}
expenditure_urban_rural<-map_to_result(data = assessment_data,
                      dependent.var = "expendituretotal",
                      independent.var = 'urbanrural',
                      case = my_case,
                      weighting = myweighter,
                      questionnaire = questionnaire)


```

## Show Results

First, we add labels to the result (assuming that you've loaded a questionnaire):

```{r, warning=F}
expenditure_urban_rural<-map_to_labeled(result = expenditure_urban_rural,
                                                questionnaire = questionnaire)
```

Finally, we can get visualisations, tables etc.:


```{r, warning=F}
chart<- map_to_visualisation(expenditure_urban_rural)
table<-map_to_table(expenditure_urban_rural)
chart
table

```


### Save/export the results
To save/export any results, you can use the generic `map_to_file` function. For example:

```{r,eval=F}
# map_to_file(results$summary.statistics,"summary_stat.csv")
# map_to_file(myvisualisation,"barchart.jpg",width="5",height="5")

```
You will find the files in your current working directory (which you can find out with `getwd()`)

## Stratified Samples
For the weighting, we'll use IMPACT's `surveyweights` package. It was installed when you installed `hypegrammaR`. Load it:
```{r}
# library(surveyweights)
```
For stratified samples, we need to provide a _sampling frame_.
```{r}
# mysamplingframe<-read.csv("../tests/testthat/test_samplingframe.csv")

```
The sampling frame must have exactly one row per stratum; one column for the strata names, one column for the population numbers. Our example data frame looks like this:

```{r}
# head(mysamplingframe)

```
The names must match _exactly_ the values in a column of the data; in this case it is `mydata$stratification`.

```{r}
# head(mydata$stratification)
```
Now we can create a "weighter" object:
```{r}
# myweighter<-weighting_fun_from_samplingframe(sampling.frame = mysamplingframe,
#                                              data.stratum.column = "stratification",
#                                              sampling.frame.population.column = "population",
#                                              sampling.frame.stratum.column = "strata.names")
```

Now we can use `analyse_indicator` just like before, but pass it the weighter we just created, so the weighting will be applied (pay attention to the last argument):

```{r}
# result<-analyse_indicator(
#                   data = mydata,
#                   dependent.var = "nutrition_need",
#                   independent.var = "region",
#                   hypothesis.type = "group_difference",
#                   independent.var.type = "categorical",
#                   dependent.var.type="numerical",
#                   weighting = myweighter)


# result$summary.statistic

```




## Cluster Samples

### without extra weighting
If the clusters don't need to be weighted (in addition to the strata), all you need is to tell `analyse_indicator` which data variable identifies the cluster:

```{r}

# result<-analyse_indicator(
#                   data = mydata,
#                   dependent.var = "nutrition_need",
#                   independent.var = "region",
#                   hypothesis.type = "group_difference",
#                   independent.var.type = "categorical",
#                   dependent.var.type="numerical",
#                   weighting = myweighter,
#                   cluster.variable.name = "village")


```


## With extra weighting
If the clustering comes with it's own weights (if records in different clusters within the same stratum had different probabilities to be selected probabilities), you need to load the sampling frame in the same way you did for the stratification, then combine the two weighting functions:

```{r,eval=F}

# samplingframe2<-read.csv("../tests/testthat/test_samplingframe2.csv")
# 
# myweighting_cluster<-weighting_fun_from_samplingframe(samplingframe2,
#                                                     data.stratum.column = "village",
#                                                     sampling.frame.population.column = "populations",
#                                                     sampling.frame.stratum.column = "village.name")
# 

# combined_weighting<-combine_weighting_functions(myweighing,myweighting_cluster)

# result<-analyse_indicator(
#                   data = mydata,
#                   dependent.var = "nutrition_need",
#                   independent.var = "region",
#                   hypothesis.type = "group_difference",
#                   independent.var.type = "categorical",
#                   dependent.var.type="numerical",
#                   weighting = combined_weighting,
#                   cluster.variable.name = "village")



```



## Using the Questionnaire
If we further load the questionnaire, we can do some extra cool stuff:

- Better analyse select_multiple questions
- Automatically identify data types
- Put proper labels on plots

### Loading the questionnaire
```{r}
require("koboquest")
# questionnaire<- load_questionnaire(mydata,
#                               questions.file = "../tests/testthat/kobo questions.csv",
#                               choices.file = "../tests/testthat/kobo choices.csv")



# result<-analyse_indicator(mydata,
#                   dependent.var = "accesstomarket",
#                   independent.var = "region",
#                   dependent.var.type = "categorical",
#                   independent.var.type = "categorical",
#                   hypothesis.type = "group_difference",
#                   weighting=myweighter)


# vis<-map_to_visualisation(result)


```


  
  
  
  
  
