---
title: "The Grammar of Hypothesis"
author: "Barner M., Henzler E."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Logic

## Main steps

Any analysis with HypegrammaR follows the same structure:

- identify the main parameters of your assesment and _load_ your *raw inputs* from csv files:
  - you *data*
  - *sampling frame(s)*
  - *questionnaire* choices and question sheet.

- decide the main parameters of your analysis:
    - what type of hypothesis do you have?
    - what are the the dependent and independent variables, and what are their data types?
- _map_ from your main parameters to a distinct *analysis case*.
- _map_ your *raw inputs* and *analysis case* to receive an analysis *result*
- _map_ your *result* to a *visualisation* / *table* or other appropriate outputs
- _map_ your outputs to a *file*


## Example

### load hypegrammaR package
```{r}
library(hypegrammaR)

```

### Load your files with the appropriate functions:
```{r}
assessment_data<-load_data(file = "../tests/testthat/data.csv")

sampling_frame<-hypegrammaR::load_samplingframe("../tests/testthat/test_samplingframe.csv")

questionnaire<-load_questionnaire(data = assessment_data,
                                             questions.file = "../tests/testthat/kobo questions.csv",
                                             choices.file = "../tests/testthat/kobo choices.csv",
                                  choices.label.column.to.use = "label::English"
                                             )


```

### _Map_ to the analysis case
You need to know:
- The hypothesis type. Currently implemented are:
  - `direct_reporting`
  - `group_difference`
- the names of the columns that are your dependent and independent variables
```{r}

case <- map_to_case(data = assessment_data,
                    hypothesis.type = "group_difference",
                    dependent.var = "number_simultaneous_unmet_need",
                    independent.var = "region")

```
### _Map_ to weighting
```{r}

weighting <- map_to_weighting( sampling.frame = sampling_frame,
                               data.stratum.column = "stratification",
                               sampling.frame.population.column = "population",
                               sampling.frame.stratum.column = "strata names",
                               data = assessment_data)

```


## Now put it all together and _Map_ to the result:

```{r}

result<-map_to_result(data = assessment_data,
              dependent.var = "number_simultaneous_unmet_need",
              independent.var =   "region",
              case = case,
              weighting = weighting)
```


## _Map_ to usable outputs
### Chart
```{r,warning=FALSE}

chart<-map_to_visualisation(result)
heatmap<-map_to_visualisation_heatmap(result)
chart
heatmap
```
### gimme Labels!
```{r,warning=FALSE}
result %>% map_to_labeled(questionnaire) -> result_labeled
chart <- result_labeled %>% map_to_visualisation
heatmap <- result_labeled %>% map_to_visualisation_heatmap


```


### Save as files

```{r, eval=FALSE}
map_to_file(chart,"barchart.jpg")
map_to_file(result$summary.statistic,"summary_statistics.csv")

```

The grammar is built from two types of elements:
- "Blocks": Take the output of a mapping
- "Mappings": Decide what to do, call a "block" that does it, and returns another block.








