---
title: "The Grammar of Hypothesis"
author: "Barner M., Henzler E."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Speaking with the Grammar of Hypothesis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Logic

## Main steps



Any analysis with HypegrammaR follows the same structure:

- Load your input data
- decide your analysis parameters
    - what type of hypothesis do you have?
    - what are the the dependent and independent variables, and what are their data types?
- _map_ from your main parameters to a distinct *analysis case*.
- _map_ your *raw inputs* and *analysis case* to receive an analysis *result*
- _map_ your *result* to a *visualisation* / *table* or other appropriate outputs
- _map_ your outputs to a *file*


## Example

### Once (ever per machine):
```{r,eval=F}
remotes::install_github('mabafaba/hypegrammaR',build_opts = c())
remotes::install_github('mabafaba/surveyweights',build_opts = c())
remotes::install_github('mabafaba/koboquest',build_opts=c())

```
### Once per Assessment

#### Load the hypegrammaR package
```{r,warning=FALSE,message=FALSE}
library(hypegrammaR)

```

#### Load your files

All input files are expected as csv files.

Each input we usually expect with an assessment has it's own function to load it. They check that the format is in line with what is expected, make sure they play well with each other and prepare the functionality they are used for.

First the data. A csv file with data in standard Kobo format.
```{r}
assessment_data<-load_data(file = "../tests/testthat/data.csv")
```

Then a sampling frame. A csv file with one column with strata names, one column with population numbers. The strata names must match exactly some values in the data. We must tell the loading function which column is what in the sampling frame.
```{r}
sampling_frame<-load_samplingframe("../tests/testthat/test_samplingframe.csv")
```

Finally the questionnaire, which depends on the question and the choices sheet as a csv.

```{r}

questionnaire<-load_questionnaire(data = assessment_data,
                                             questions.file = "../tests/testthat/kobo questions.csv",
                                             choices.file = "../tests/testthat/kobo choices.csv",
                                  choices.label.column.to.use = "label::English"
                                             )

```


#### _Map_ to weighting
```{r}

weighting <- map_to_weighting( sampling.frame = sampling_frame,
                               data.stratum.column = "stratification",
                               sampling.frame.population.column = "population",
                               sampling.frame.stratum.column = "strata names",
                               data = assessment_data)

```

### For each Hypothesis

### _Map_ to the analysis case
You need to know:

- The hypothesis type. Currently implemented are:
  - `direct_reporting`
  - `group_difference`
- the names of the columns that are your dependent and independent variables

```{r}

case <- map_to_case(hypothesis.type = "group_difference",
                    dependent.var.type = "numerical",
                    independent.var = "categorical")

```


## Now put it all together and _Map_ to the result:

```{r}

result<-map_to_result(data = assessment_data,
              dependent.var = "number_simultaneous_unmet_need",
              independent.var =   "region",
              case = case,
              weighting = weighting)
```

## Add labels

## _Map_ to usable outputs
### Chart
```{r,warning=FALSE}

chart<-map_to_visualisation(result)
heatmap<-map_to_visualisation_heatmap(result)
chart
```
### gimme Labels!
```{r,warning=FALSE}
result %>% map_to_labeled(questionnaire) -> result_labeled
chart <- result_labeled %>% map_to_visualisation
heatmap <- result_labeled %>% map_to_visualisation_heatmap


```


### Save as files

```{r, eval=FALSE}
map_to_file(chart,"barchart.jpg")
map_to_file(result$summary.statistic,"summary_statistics.csv")

```

The grammar is built from two types of elements:
- "Blocks": Take the output of a mapping
- "Mappings": Decide what to do, call a "block" that does it, and returns another block.








